Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-30 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, \textcolor{red}{because the field temperature is higher that the nominal or laboratory temperature, and PV system is temperature dependent,} as 
%
\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}

@@

Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE) or Life Cycle Cost (LCC). Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{APPLYING AUTOMATED VERIFICATION TO OPTIMAL SIZING OF STAND-ALONE PV SYSTEMS}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to optimize stand-alone PV systems using automated verification. 
%
 \begin{algorithm}
 \caption{Optimization algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $initialize \, variables$ \\
  \STATE $declare \, list \, of \, PV \, panels \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, controllers \, data \, and \, cost $ \\
  \STATE $declare \, list \, of \, batteries \, data \,  and \, cost $ \\
  \STATE $declare \, list \, of \, inverters \, data \,  and \, cost $ \\
  \STATE $declare \, the \, maximum \, cost \, possible \, MaxCost $  \\
  \STATE $declare \, power \, demand, \, power \, peak, \, energy \, consumption $ \\
  \STATE $declare \, battery\,  autonomy, deep \, of \, discharge, AC \, voltage$ \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE $declare \, non-det \, variable \, to \, select \, Panel \, from \, list$ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Controller \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Battery \, from \, list $ \\
 	\STATE $declare \, non-det \, variable \, to \, select \, Inverter \, from \, list $ \\ 	
 	\STATE $calculate \, E_{corrected}, \, E_{p} $ \\
	\STATE $calculate \, N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE $calculate \, C_{bank}$ \\
	\STATE $calculate \, N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{c})$ \\
 	\STATE $calculate \, I_{sc,amb}$ \\
 	\STATE $calculate \, I_{c,min}$ \\
 	\STATE $requeriment \, enforced \, by \, \textbf{assume}(I_{c})$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{in}DC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(V_{out}AC)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(Demand)$ \\
	\STATE $requeriment \, enforced \, by \, \textbf{assume}(P_{surge})$ \\
	\STATE $non-det \, variables \, hold \, feasible \, equipment \, and \ cost $ \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE $Violation \, check \, with \, \textbf{assert}(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

Our algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5). After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8. The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, stating that the automatic verification reached a \textit{SAT} (satisfiable) condition. The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13). That procedure ensures that the automated verification checks all possibilities of items from each equipment, and combine them to assemble a feasible PV solution, which meets the user requirements.

@@

If our algorithm does not find a feasible solution among the item of equipment that were inputted to the code, then the result is an \textit{UNSAT}, i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution.

\textcolor{red}{The main challenge for the verification part is to found a feasible solution (technically speaking, regarding the constraints and user requirements) that is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is inputted to the tool}.
%---------------------------------------------------------------------------
\section{RESULTS AND DISCUSSION}
%---------------------------------------------------------------------------
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The experiments were performed with a predefined timeout of 240 minutes.

>>>>

The short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent, as 
%
\begin{equation}
\label{eq:iscamb}
\scriptstyle I_{sc,amb} = \dfrac{\scriptstyle G}{\scriptstyle G_{ref}} \left[ \scriptstyle I_{sc,ref} + \scriptstyle \mu_{I} \scriptstyle \times \scriptstyle (T-25) \right]. 
\end{equation}

@@

Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the local of deployment is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes the pseudocode used to symthesize stand-alone PV systems using software model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels data and cost \\
  \STATE Declare list of controllers data and cost \\
  \STATE Declare list of batteries data and cost \\
  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare nondet variable to select PV Panel from list \\
 	\STATE Declare nondet variable to select Controller from list \\
 	\STATE Declare nondet variable to select Battery from list \\
 	\STATE Declare nondet variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requeriment enforced by \textbf{assume}$(I_{c})$ \\
	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC)$ \\
	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requeriment enforced by \textbf{assume}$(Demand)$ \\
	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-det variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

Our synthesis algorithm starts with the input of manufacturers data and prices of PV panels, batteries, charge controllers and inverters (Lines 2 to 5). After that, we define user requirements, i.e., house requirements and design definitions, from Lines 6 to 8. The \textit{for}-loop started at Line 9 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the assertion stated in Line 28; if that happens, then our algorithm has found an optimal solution, thereby stating that the automatic verification reached a \textit{SAT} (satisfiable) condition. The algorithm uses non-deterministic variables to choose one specific data from a list of PV panels, controllers, batteries and inverters (Lines 10 to 13). That procedure ensures that the automated verification checks all possibilities of items from each equipment, and combine them to assemble a feasible PV solution, which meets the user requirements.

@@

If our algorithm does not find a feasible solution among the item of equipment that were provided to our synthesis algorithm, then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the itens of each equipment and create a feasible solution. The main challenge for the verification part is to find a feasible solution (technically speaking, regarding the constraints and user requirements), which is the best financial solution at the same time (lowest cost of deployment) from a list of equipment and components that is provided to our synthesis algorithm. \textcolor{red}{An unfeasible solution happens due to the incomplete list of equipment?}
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The experiments were performed with a predefined timeout of 240 minutes.
